---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# capcom

[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html) 
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
```{r, echo = FALSE}                                                                                                       
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])                                                                 
version <- gsub('-', '.', version)                                                                                         
```                                                                                                                        
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![Project Status: Inactive – The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)

The goal of capcom is to provide utility functions to power Internetrix 
digital data analysis activities and shiny applications.   

Most of the functions are set to work with data from the Google Analytics API
and perform an opinionated and specific analysis task.  

## Installation

You can install the released version of capcom from [Github](https://github.com/Internetrix/capcom) with:

``` r
devtools::install_github('Internetrix/capcom')
```


